Reproductive Allocation Calculations

### 2015-03-25 leaflifespan.Rmd
Change variable name tag_ID -> individual (cases missed in earlier commit)
continud work on script

@@

#harvest summary by species, age
harvest_summary <- harvest %>%
  group_by(species, age) %>%
  summarise_each(funs(mean, se, length), total_stem_weight, total_leaf_weight, height)

@@

plot(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==7), xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA", las=1, pch=16)
text(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-0.9, cex=0.9,col="blue")
text(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==7 & species=="HATE"), labels=species, pos=1, offset=-0.9, cex=0.9,col="red")
mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,species!="HATE" & age==7))
summary(mod)
abline(mod)
```

@@

#where does the [spp] comes from? This is the first place in the script it is used like this - I assume it could be any name?
plot_LLvAge <- function(spp) {
  plot(LL_birth ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
     main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
}

@@

#plots regressing variables against one another
```{r, echo=FALSE,results='hide', message=FALSE}
plot(change_shoot_area~new_length,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8, xlab="shoot extension (mm)", ylab="increased shoot cross sectional area")
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod <- lm(change_shoot_area~new_length +age,data=subset(SummaryInd,change_shoot_area<1000000))
summary(mod)

>>>>

technical:
-parts remake not working
-tag_ID still exists in 1 file
-avoiding duplicate columns with name "age" "species" (how to subset columns that are merged, how to delete columns)
-getting model summaries to show up when looping through species/ages

@@

#harvest summary by species, age
harvest_summary <- harvest %>%
  group_by(species, age2) %>%
  summarise_each(funs(mean, se, length), total_stem_weight, total_leaf_weight, height)

@@

plot(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==5), xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA", las=1, pch=16)
text(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-0.9, cex=0.9,col="blue")
text(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==5 & species=="HATE"), labels=species, pos=1, offset=-0.9, cex=0.9,col="red")
mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,species!="HATE" & age==5))
summary(mod)
abline(mod)
```

@@

plot_LLvAge <- function(spp) {
  plot(LL_birth ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
     main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
}

@@

#models looking at how the relationship between leaf weight (or area) and total plant weight shifts with age
this should be another way to get at the decreasing "leafiness" of plants with age

```{r, echo=FALSE,results='hide', message=FALSE}
plot(leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod <-lm(FinalWeight~leaf_weight+age+species,SummaryInd)
summary(mod)

plot_LeafWeight <- function(spp) {
  plot(leaf_weight~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
  legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
  mod <-lm(FinalWeight~leaf_weight+age,data=subset(SummaryInd,species==spp))
  abline(mod)
  summary(mod)
}

for(n in names(labels.spp)) {
  plot_LeafWeight(n)

#plot looking at leaf area versus plant weight
#USE THIS PLOT IN LAB MEETING - CLEARLY SHOWS DECLINE IN INTERCEPT WITH AGE  
plot(leafArea~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod <-lm(FinalWeight~leafArea+age+species,SummaryInd)
summary(mod)

plot_LeafArea <- function(spp) {
  plot(leafArea~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
  legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
  mod <-lm(FinalWeight~leafArea+age,data=subset(SummaryInd,species==spp))
  abline(mod)
  summary(mod)
}

for(n in names(labels.spp)) {
  plot_LeafArea(n)
}

#plots looking at shoot extension versus plant size
plot(new_length~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod <-lm(FinalWeight~new_length+age+species,SummaryInd)
summary(mod)

plot_LeaderExtension <- function(spp) {
  plot(new_length~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
  legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
  mod <-lm(FinalWeight~new_length+age,data=subset(SummaryInd,species==spp))
  abline(mod)
  summary(mod)
}

for(n in names(labels.spp)) {
  plot_LeaderExtension(n)
} 
```

#many plots regressing variables against one another
```{r, echo=FALSE,results='hide', message=FALSE}
plot(change_shoot_area~new_length,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8, xlab="shoot extension (mm)", ylab="increased shoot cross sectional area")
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod <- lm(change_shoot_area~new_length +age,data=subset(SummaryInd,change_shoot_area<1000000))
summary(mod)
